---
title: "CodeBook"
author: "ramya"
date: "Sunday, November 23, 2014"
output: html_document
---
This is the code book for the tidy data set present in the file 'TidyData.txt'. 
This data has been obtained from merging and manipulating data available from https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip.

The script to manipulate data is - run_analysis.R

```{r echo=FALSE,warning=FALSE}
source("run_analysis.R")
```
###Descriptive activities names used in the Tidy data set.
There are six acctivitesfor which the measurements are obtained, the activities are the following.
```{r}
unique(newset$ActivityName)

```

###Descriptive names/labels for the variables (columns in the tidy data set) 
The training and test data are combined to form tidy data. 
The Subject column indicates the participants, each participant is marked as Subject x where x is a numeric indicating the participant id. 
The ActivityName column indicates the activity consideredfor that row. 

These signals were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.
Various features are considered and for each feature the mean value and the standard deviation are calculated, for the three X, Y, Z axis.Following are the list of features considered,
TimeBodyAccelerometer
TimeGravityAccelerometer
TimeBodyAccelerometerJerk
TimeBodyGyroscope
TimeBodyGyroscopeJerk
TimeBodyAccelerometerMagnitude
TimeBodyGyroscopeMagnitude
TimeBodyGyroscopeJerkMagnitude
FrequencyBodyAccelerometer
FrequencyBodyAccelerometerJerk
FrequencyBodyGyroscope
FrequencyBodyAccelerometerMagnitude
FrequencyBodyBodyAccelerometerJerkMagnitude
FrequencyBodyBodyGyroscopeMagnitude
FrequencyBodyBodyGyroscopeJerkMagnitude

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals. Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm.Finally a Fast Fourier Transform (FFT) was applied to some of these signals.

More details about the features can be found at - http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones


Below is the list of all columns present in the tidy data
```{r}
names(newset)
```

###Summary of the tidy data set
```{r}
summary(newset)
```

###Sample of the tidy data set created
```{r}
head(newset)

```
